Spin canonical divisors of log stacky curves

### 2015-06-25 stacky_write_up/spin_cring.tex
replace symbols with words in deg1_sat_ind
added genus 1 proof

Folloing Voight and Zureick-Brown, \cite{vzb:stacky}, we examine a much more general setting, generalizing Petri's theorem in many directions.
A divisor $\Delta \in d X$ is a {\bf log divisor} if $\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct. Let $(\sx,\Delta)$ denote a tame seperably rooted stacky curve over a field $k$ so that $X$ is the coarse space of $\sx$, as defined in \cite[Section 5.2]{vzb:stacky} so that $\di \sx = \div X \bigoplus_{i=1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$. Let $K_\sx = K_X + \sum_{i=1}^{r}\frac{e_i-1}{e_i}P_i.$ In this case, we say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$. Call $\halfcan \in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$, be a divisor $\halfcan \in \di \sx$ so that $2\halfcan \sim K_\sx + \Delta.$ If $X$ has genus $g$ and $\delta = \deg \Delta,$ then we say $\sx$ has signature $(g; e_1, \ldots, e_r;\delta)$. A {\bf log spin curve} is a triple $(X,\Delta,\halfcan)$ where $(X,\Delta)$ and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$. The central object of study in this paper is the {\bf log spin canonical ring} of $(X,\Delta,L)$ is
\begin{align*}
	R(X,\Delta,L) = \bigoplus_{n \geq 0} H^0(X,nL)
\end{align*}

@@

\noindent
is generated as a $k$-algebra by elements of degree at most $e =
\max(5, e_1, \ldots, e_r).$ If the genus $g \geq 2,$ and $\Delta = 0$ then 
$R(\sx,\Delta, \halfcan)$ has relations in degree at most $\max(11, e_1,
\ldots, e_r).$ Otherwise, $R(\sx, \Delta, \halfcan)$ has relations in degree at most
$\max(10, e_1, \ldots, e_r),$ so long as $\sigma$ does not lie in a finite list of
exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}
for signatures with $g = 1$ and Table ~\ref{table:g_0_exceptional}
for signatures with $g = 0$.
\end{thm}
\todo{Say that this follows immediately from the three theorems for the special cases.}
Note that in the course of the proof of Theorem ~\ref{thm:g_0_generators_relations} we will not merely obtain bounds on the degrees of the generators and relations. In fact, if the genus $g = 0$ or $g = 1$, the proof yields an explicit system of generators and the initial ideal of relations. While in the genus $g \geq 2$ case, the proof does not always yield an explicit system of generators and relations, if the halfcanonical divisor $\halfcan$ can be written as $\halfcan' + \Lambda$ with $(\halfcan',0,X)$ a log spin curve, and a system of generators and relations for $\halfcan'$ is known, then our proof provides an inductive procedure for determining the generators and initial ideal of relations for $\halfcan$. In fact, such a system of generators and relations are known for $\halfcan'$ in many cases, as detailed in Neves ~\cite[Section III.4]{neves:halfcan}.

@@

\ssec{Inductive Lemmata: Adding Points}
\label{ssec:add_pts}
In this section, we prove various inductive statements under the following setup:
Let $\halfcan'$ be $\mathbf{Q}$-divisor of $X$ (and often a log half canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbf{N}$ and certain saturation conditions.  Let $\halfcan=\halfcan'+P$ for some $P$ not in the support of $\halfcan$.\todo{do we always assume this?}  Then we will explicitly describe elements that minimally generate $R_\halfcan$ over $\halfcan$' and initial terms of relations that minimally generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Grobner Basis).   The proofs of these lemmas all follow similar patterns, so we will present a few \todo{give the precise number we show} and leave the rest to the reader.

@@

\begin{lem}
\label{lem:deg1-sat-ind}
Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as
defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
satisfying $h^0(X, \lfloor{D}\rfloor)\ge 1$.  Suppose $P$ is not a base-point of $dD$ for all $d\in \mathbf{N}^+$ meaning that $R_D$ has generically chosen generators (in the appropriate respective degrees)
$u, x_1, \ldots, _m$ all with $\ord_P=0$ and such that $\deg(u)=1$.  Let $D$ be generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
in degree at most $\bar{\tau}$, where all $x_i$s also satisfy $\ord_P(u)(x_i)$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
for some $\alpha,\beta \in \mathbf{N}$ such that
\begin{equation}
\label{eqn:deg1_sat_ind_dim}
	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \; \forall d \in \mathbf{
	N} : d \ge \frac{\beta}{\alpha}.
\end{equation}
Let 
\[
	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
\]
be the non-negative best lower approximation.
Then 
\begin{itemize}
\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
degree $d_i$ and has a pole at $P$ of degree $c_i$

@@

Begin by focusing on the $d^{\text{th}}$ component of $R_{D'}$: $(R_
{D'})_d = H^0(X, \lfloor D + \frac{\alpha}{\beta} P \rfloor)$. By
our hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d
\in \mathbf{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,

@@

%If the genus of $X$ is 0 and $D\sim\sum \frac{\alpha_i}{\beta_i} P_i$ is linearly equivalent to an effective $\mathbf{Q}$ divisor of $X$, then $R_D$ is generated in degree at most $\max(\beta_i,1)$ with relations generated in degree at most $2\max(\beta_i,1)$.

@@

%coefficient lying in $\mathbf{Z}[\frac{1}{e_i}]$ (ranging over $e_i$

@@

Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx',J)$
to be {\bf admissible} if the $R'$ admits a presentation

\begin{align*}
	R' \cong \left( k[x_1, \ldots, x_m] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
\end{align*}

@@

\begin{lem}\label{lem:n-3s-admissible}
Let $(\sx', L', \Delta), (\sx, L,\Delta)$ be log stacky curve with log half-canonical divisors $L'$ and $L$ with signatures $(g; e_1, \ldots, e_{r-1}; \delta)$ and $(g; e_1, \ldots, e_r; \delta)$ with all $e_i=3$ and $L=L'+\frac{1}{3}P$ for some point $P$.  Then if $\{e_1,...,e_{r-1}\}$ in has any nontrivial admissible subset, then any subset of $\{e_1,...,e_r\}$ is admissible.
\end{lem}
\begin{proof}\todo{proof}

@@

Second, suppose $H^0(X,L) = 0$.
Note that because $\deg 3L = 3$, we have by Riemann--Roch that $H^0(X,3L) = 2$. 
Note additionally that $3L \sim K + L \sim 2P_1 + L$. Since $3L$ is base point free, by Riemann--Roch
we have that there exists a rational function $f$ with $\div f|_{2P_1 + L} = -2P_1 - L.$ Additionally, there are no functions $g \in H^0(X,L + 2P_1)$ 
with $\di g|_{2P_1 + L} = -L,$ since $H^0(X,L) = 0.$ Therefore, there must 
exist a function $h \in H^0(X,L+2P_1)$ so that $\di h|_{L + 2P_1} = -L - P_1$.
Then, $h \cdot f \in H^0(X,2L + 4P_1) \cong H^0(X,6L)$ has a pole of odd 
order at $P_1$, and is therefore independent from the image of $\sym^3 H^0(X,3L)$.
\end{proof}

@@

In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution. We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_order_ind} and add additional points using Lemma ~\ref{lem:deg1-sat-ind} and Lemma ~\ref{lem:sat-two-induction-high-genus}.

@@

\begin{enumerate}
	\item $\halfcan' = 0$
	\item $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_3.$
\end{enumerate}

@@

\begin{example}
\label{eg:base-1-33}
Let $\sx'$ be a stacky curve so that $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2$. In this example, we show
$$R_{\halfcan'} \cong k[u,x_3,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u)$$
and that $(\sx',\{3,3\})$ is admissible.

Let $u \in H^0(\sx,2\halfcan')$ be any nonzero element, let $x_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P$ but not at $Q$ and $y_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $Q$ but not at $P$. Let $y_4 \in H^0(\sx,3\halfcan')$ be an element with a pole of order 1 at both $P$ and $Q$. Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q + R_1, 3P - 3Q + R_2$ are one dimensional, while the linear system $3P - 3Q \sim P-Q$ is zero dimensional.

@@

We next check $(\sx',\{3,3\})$ is admissible. We clearly have two generators $x_3,y_3$ in degree 3 with a pole of order $\frac{3-1}{2}$ by construction. Hence, (Ad-i) holds. We next check (Ad-ii) for the point $R_1$, as the case of $R_2$ is symmetric. Here, by construction
$$
\frac{-\ord_{R_1}(z)}{\ord(z)} = \begin{cases}
	0 &\text{ if }z \in \{u,y_3\}\\
	\frac{1}{4} &\text{ if }z = y_4
\end{cases}.$$
Since $0 < \frac{1}{4} < \frac{1}{3}$, (Ad-ii) holds.
Finally, to check (Ad-iii) note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = 2 \cdot 1 -1 + 0$.
\end{example}

\ssec{Genus One Exceptional Cases}

\todo{remove stuff about tame and separably rooted, change to $\BQ$ divisor.}
Let $\sx$ be a tame, seperably rooted stacky curve of genus 1. Let $P,Q$ are distinct hyperelliptic fixed points, and $R$ be a point on $\sx$.

\todo{cite genus 1 final theorem here, to explain what these cases are exceptional to}
\begin{longtable}	{| c || c | c | c |}
	\hline
	L' & Generator Degrees & Degrees of Minimal Relations \\
	\hline
	\hline
	$(1;-; 0)$ & $\{2\}$ & $\emptyset$ \\	\hline

	$(1; 3; 0)$ & $\{2,3,7\}$ & $\{14\}$ \\	\hline

	$(1; 5; 0)$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline

@@

We now elaborate on the computation of the results in 
Table ~\ref{table:g-1-exceptional}. In the following example we will explain the case $\sigma = (1;5;0)$ as the other cases are even easier.

@@

\begin{example}
\label{eg:exception-1-e}
Let $L = P - Q + \frac{e-1}{2e}R_1.$ Here, we claim $R_L \cong k[u,y_3, y_5, \ldots, y_e]/I_e,$ where we define $I_5 = y_3^4 - uy_5^2$ and $I_e$ is inductively defied via Theorem ~\ref{thm:ram_order_ind} so that $in(I_e) = in(I_{e-2})k[u, y_3,\ldots, y_e] + \langle y_e z \mid z \neq y_e, y_{e-2} \rangle.$
Furthermore, $\deg u = 2, \deg y_i = i$.
\todo{Note that here there is a quartic generator of $I$ in degree 12, providing exceptions to minimality by quadrics and an exception to the relation bound when $e = 5$.}
\end{example}
\fi

\begin{example}
\label{eg:exception-1-5}
Let $L = P - Q + \frac{2}{5}R_1$ be a half canonical divisor on a stacky curve $\sx$. Let $u \in (R_L)_1$ be any nonzero element. We obtain $\di u|_R = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch $\dim_k (R_L)_1 = 1$ let $y_3 \in (R_L)_3$ be any nonzero element. We obtain $\di y_3|_R = - R,$ by Riemann Roch, since if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0(\sx,3P-3Q) \cong H^0(\sx,P-Q) \cong 0$ as $P \neq Q$. Finally, let $y_5 \in (R_L)_5$ be an element with $y_5|_R = -R$. Then, we claim there is some $\alpha \in k$ so that
$R_L \cong k[u,y_3, y_5]/(y_3^4 - \alpha uy_5^2).$
The proof of this can be gotten by first using Riemann--Roch and counting the pole order at $R$ considerations to check the above relation exists, and that the generators and relation determine a ring whose $k$th graded piece has the same dimension of $R_L$. It is analogous to Example ~\ref{ex:base-377}, and is omittied.
\end{example}

@@

\begin{thm}
\label{thm:g_1_generators_relations}
Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$,
so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$.
If $g = 1$, then the canonical ring

\noindent
is generated as a $k$-algebra by elements of degree at most $e =
\max(5, e_1, \ldots, e_r)$ and has relations in degree at most $\max
(10, e_1, \ldots, e_r),$ so long as $\sigma$ does not lie in a
finite list of exceptional cases, as listed in Table
~\ref{table:g-1-exceptional}.
\end{thm}

>>>>

Folloing Voight and Zureick-Brown, \cite{vzb:stacky}, we examine a much more general setting, generalizing Petri's theorem in many directions.
A divisor $\Delta \in d X$ is a {\bf log divisor} if $\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct. Let $(\sx,\Delta)$ denote a tame seperably rooted stacky curve over a field $k$ so that $X$ is the coarse space of $\sx$, as defined in \cite[Section 5.2]{vzb:stacky} so that $\di \sx = \di X \bigoplus_{i=1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$. Let $K_\sx = K_X + \sum_{i=1}^{r}\frac{e_i-1}{e_i}P_i.$ In this case, we say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$. Call $\halfcan \in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$, be a divisor $\halfcan \in \di \sx$ so that $2\halfcan \sim K_\sx + \Delta.$ If $X$ has genus $g$ and $\delta = \deg \Delta,$ then we say $\sx$ has signature $(g; e_1, \ldots, e_r;\delta)$. A {\bf log spin curve} is a triple $(X,\Delta,\halfcan)$ where $(X,\Delta)$ and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$. The central object of study in this paper is the {\bf log spin canonical ring} of $(X,\Delta,L)$ is
\begin{align*}
	R(X,\Delta,L) = \bigoplus_{n \geq 0} H^0(X,nL)
\end{align*}

@@

\noindent
is generated as a $k$-algebra by elements of degree at most $e =
\max(5, e_1, \ldots, e_r).$ If the genus $g \geq 2,$ and $\Delta = 0$ then 
$R(\sx,\Delta, \halfcan)$ has minimal relations in degree at most $\max(11, 2e_1,
\ldots, 2e_r).$ Otherwise, $R(\sx, \Delta, \halfcan)$ has minimal relations in degree at most
$\max(10, 2e_1, \ldots, 2e_r),$ so long as $\sigma$ does not lie in a finite list of
exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}
for signatures with $g = 1$ and Table ~\ref{table:g_0_exceptional}
for signatures with $g = 0$.
\end{thm}
\todo{Say that this follows immediately from the three theorems for the special cases.}
Note that in the course of the proof of Theorem ~\ref{thm:g_0_generators_relations} we will not merely obtain bounds on the degrees of the generators and relations. In fact, if the genus $g = 0$ or $g = 1$, the proof yields an explicit system of generators and the initial ideal of relations. While in the genus $g \geq 2$ case, the proof does not always yield an explicit system of generators and relations, if the halfcanonical divisor $\halfcan$ can be written as $\halfcan' + \Lambda$ with $(\halfcan',0,X)$ a log spin curve, and a system of generators and relations for $\halfcan'$ is known, then our proof provides an inductive procedure for determining the generators and initial ideal of relations for $\halfcan$. In fact, such a system of generators and relations are known for $\halfcan'$ in many cases, as detailed in Neves ~\cite[Section III.4]{neves:halfcan}.

@@

\ssec{Inductive Lemmata: Adding Points}
\label{ssec:add_pts}
In this section, we prove various inductive statements under the following setup:
Let $\halfcan'$ be $\mathbb{Q}$-divisor of $X$ (and often a log half canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions.  Let $\halfcan=\halfcan'+P$ for some $P$ not in the support of $\halfcan$.\todo{do we always assume this?}  Then we will explicitly describe elements that minimally generate $R_\halfcan$ over $\halfcan$' and initial terms of relations that minimally generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Grobner Basis).   The proofs of these lemmas all follow similar patterns, so we will present a few \todo{give the precise number we show} and leave the rest to the reader.

@@

\begin{lem}
\label{lem:deg1-sat-ind}
Let $X$ be a genus $g$ curve with a $\mathbb{Q}$-divisor $D$ (as
defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
satisfying $h^0(X, \lfloor{D}\rfloor)\ge 1$.  Suppose $P$ is not a base-point of $dD$ for all $d\in \mathbb{N}^+$ meaning that $R_D$ has generically chosen generators (in the appropriate respective degrees)
$u, x_1, \ldots, x_m$ all with $\ord_P(u) =0$ \todo{Aaron: Instead of having $\deg u = 0$, don't we only need that $\ord_P(u) = \lfloor D|_P \rfloor$?} and $\deg(u)=1$. Let $D$ be generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated
in degree at most $\bar{\tau}$, where all $x_i$ also satisfy $\ord_P(u)(x_i)$. \todo{Aaron: What does $\ord_P(u)(x_i)$ mean?}  Suppose $D' = D + \frac{\alpha}{\beta} P$
for some $\alpha,\beta \in \mathbb{N}$ such that
\begin{equation}
\label{eqn:deg1_sat_ind_dim}
	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \; \forall d \in \mathbb{
	N} : d \ge \frac{\beta}{\alpha}.
\end{equation}
\label{eqn:deg1-sat-ind}
Let 
\[
	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
\]
be the non-negative best lower approximation.
Then 
\begin{itemize}
\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
degree $d_i$ and has a pole at $P$ of degree $c_i$

@@

Begin by focusing on the $d^{\text{th}}$ component of $R_{D'}$: $(R_
{D'})_d = H^0(X, \lfloor D + \frac{\alpha}{\beta} P \rfloor)$. By
our hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d
\in \mathbb{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,

@@

%If the genus of $X$ is 0 and $D\sim\sum \frac{\alpha_i}{\beta_i} P_i$ is linearly equivalent to an effective $\mathbb{Q}$ divisor of $X$, then $R_D$ is generated in degree at most $\max(\beta_i,1)$ with relations generated in degree at most $2\max(\beta_i,1)$.

@@

%coefficient lying in $\mathbb{Z}[\frac{1}{e_i}]$ (ranging over $e_i$

@@

Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx',J)$
to be {\bf admissible} if the $R'$ admits a presentation
\todo{We should incorporate dependence on $L$ into the definition of admissible.}
\begin{align*}
	R' \cong \left( k[x_1, \ldots, x_m] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
\end{align*}

@@

\begin{lem}\label{lem:n-3s-admissible}
Let $(\sx', L', \Delta), (\sx, L,\Delta)$ be log stacky curve with log half-canonical divisors $L'$ and $L$ with signatures $(g; e_1, \ldots, e_{r-1}; \delta)$ and $(g; e_1, \ldots, e_r; \delta)$ with all $e_i=3$ and $L=L'+\frac{1}{3}P$ for some point $P$.  Then if $\{e_1,...,e_{r-1}\}$ in has any nontrivial admissible subset, then any subset of $\{e_1,...,e_r\}$ is admissible.
\todo{Aaron: Is this actually true? Shouldn't we say that if $(\sx',\{e_1,...,e_{r-1}\})$ is admissible then so is $(\sx,\{e_1,...,e_r\})$?}
\end{lem}
\begin{proof}\todo{proof}

@@

Second, suppose $H^0(X,L) = 0$.
Note that because $\deg 3L = 3$, we have by Riemann--Roch that $H^0(X,3L) = 2$. 
Note additionally that $3L \sim K + L \sim 2P_1 + L$. Since $3L$ is base point free, by Riemann--Roch
we have that there exists a rational function $f$ with $\di f|_{2P_1 + L} = -2P_1 - L.$ Additionally, there are no functions $g \in H^0(X,L + 2P_1)$ 
with $\di g|_{2P_1 + L} = -L,$ since $H^0(X,L) = 0.$ Therefore, there must 
exist a function $h \in H^0(X,L+2P_1)$ so that $\di h|_{L + 2P_1} = -L - P_1$.
Then, $h \cdot f \in H^0(X,2L + 4P_1) \cong H^0(X,6L)$ has a pole of odd 
order at $P_1$, and is therefore independent from the image of $\sym^3 H^0(X,3L)$.
\end{proof}

@@

In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution. We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_ordeP_ind} and add additional points using Lemma ~\ref{lem:deg1-sat-ind} and Lemma ~\ref{lem:sat-two-induction-high-genus}.

@@

\begin{longtable}	{| c || c | c | c |}
	\hline
	L' & Generator Degrees & Degrees of Minimal Relations \\
	\hline
	\hline
	$0$ & $\{1\}$ & $\emptyset$ \\	\hline

	$P-Q + \frac{2}{5}P_1$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline

	$\frac{3}{7}P_1$ & $\{1,5,7\}$ & $\{15\}$ \\	\hline

	$P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$ & $\{2, 3, 3, 4\}$ & $\{6,8\}$ \\	\hline
	$\frac{1}{3}P_1 + \frac{1}{3}P_2$ & $\{1, 3, 3\}$ & $\{6\}$ \\	\hline

@@

\begin{example}
\label{eg:base-1-33}
Let $\sx'$ be a stacky curve so that $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show
$$R_{\halfcan'} \cong k[u,x_3,y_3,y_4]/(x_3 y_3- \alpha uy_4,y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
and that $(\sx',\{3,3\})$ is admissible.

Let $u \in H^0(\sx,2\halfcan')$ be any nonzero element, let $x_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P$ but not at $Q$ and $y_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $Q$ but not at $P$. Let $y_4 \in H^0(\sx,3\halfcan')$ be an element with a pole of order 1 at both $P$ and $Q$. Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q + P_1, 3P - 3Q + P_2$ are one dimensional, while the linear system $3P - 3Q \sim P-Q$ is zero dimensional.

@@

We next check $(\sx',\{3,3\})$ is admissible. We clearly have two generators $x_3,y_3$ in degree 3 with a pole of order $\frac{3-1}{2}$ by construction. Hence, (Ad-i) holds. We next check (Ad-ii) for the point $P_1$, as the case of $P_2$ is symmetric. Here, by construction
$$
\frac{-\ord_{P_1}(z)}{\ord(z)} = \begin{cases}
	0 &\text{ if }z \in \{u,y_3\}\\
	\frac{1}{4} &\text{ if }z = y_4
\end{cases}.$$
Since $0 < \frac{1}{4} < \frac{1}{3}$, (Ad-ii) holds.
Finally, to check (Ad-iii) note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = 2 \cdot 1 -1 + 0$.
\end{example}

\begin{example}
\label{eg:exception-1-5}
Let $L' = \frac{2}{5}P_1$ be a half canonical divisor on a stacky curve $\sx$. Let $u \in (P_L)_1$ be any nonzero element. We obtain $\di u|_{P_1} = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch $\dim_k (P_L)_1 = 1.$ Let $y_3 \in (R_L)_3$ be any nonzero element. We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0(\sx,3P-3Q) \cong H^0(\sx,P-Q) \cong 0$ as $P \neq Q$. Finally, let $y_5 \in (R_L)_5$ be an element with $y_5|_{P_1} = -P_1$. Then, we claim there is some $\alpha \in k$ so that
$R_L \cong k[u,y_3, y_5]/(y_3^4 - \alpha uy_5^2).$
The proof of this can be gotten by first using Riemann--Roch and counting the pole order at $P_1$ considerations to check the above relation exists, and that the generators and relation determine a ring whose $k$th graded piece has the same dimension of $R_L$. It is analogous to Example ~\ref{ex:base-377}, and is omittied.

Note that $L'$ is admissible, as can be checked in a fashion analogous to the verification in Example ~\ref{eg:base-1-33}.

Finally, note that this particular case is also exceptional, because there is a relation in degree $12 > 2 \cdot 5$, but once $e' = 5$ is incremented to $e = e'+2 = 7,$ using Theorem ~\ref{thm:ram_order_ind}, this relation in degree 12 caries over, and so the case $L' = P - Q + \frac{3}{7}P_1$ is not exceptional because $12 < 2 \cdot 7$.
\end{example}

\iffalse
The base case of $L' = \frac{3}{7}P_1$ has $R_L \cong k[u,y_5,y_7]/(y_5)^3 - uy_7^2.$ 
\fi

The base cases of $L' = \frac{3}{7}P_1$ and $L' = \frac{1}{3}P_1 +\frac{1}{3}P_2$ can be similarly computed. Note this is yet another exceptional case.

\ssec{Genus One Exceptional Cases}
\label{ssec:g-1-exceptional}
\todo{remove stuff about tame and separably rooted, change to $\BQ$ divisor.}
Let $\sx$ be a tame, seperably rooted stacky curve of genus 1. Let $P,Q$ are distinct hyperelliptic fixed points, and $R$ be a point on $\sx$.

\todo{cite genus 1 final theorem here, to explain what these cases are exceptional to}
\begin{longtable}	{| c || c | c | c |}
	\hline
	L' & Generator Degrees & Degrees of Minimal Relations \\
	\hline
	\hline
	$P-Q$ & $\{2\}$ & $\emptyset$ \\	\hline

	$P-Q + \frac{1}{3}P_1$ & $\{2,3,7\}$ & $\{14\}$ \\	\hline

	$P-Q + \frac{2}{5}P_1$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline

	$\frac{1}{3}P_1$ & $\{1,6,9\}$ & $\{18\}$ \\	\hline

	$\frac{2}{5}P_1$ & $\{1,5,8\}$ & $\{16\}$ \\	\hline

	$\frac{3}{7}P_1$ & $\{1,5,7\}$ & $\{15\}$ \\	\hline

@@

We now elaborate on the computation of the results in 
Table ~\ref{table:g-1-exceptional}. We have already explained the case of 
$L' = P-Q + \frac{1}{5}P_1$ above in Example ~\ref{eg:exception-1-5}. The other cases are similar.

@@

\begin{example}
\label{eg:exception-1-e}
Let $L = P - Q + \frac{e-1}{2e}P_1.$ Here, we claim $R_L \cong k[u,y_3, y_5, \ldots, y_e]/I_e,$ where we define $I_5 = y_3^4 - uy_5^2$ and $I_e$ is inductively defied via Theorem ~\ref{thm:ram_order_ind} so that $in(I_e) = in(I_{e-2})k[u, y_3,\ldots, y_e] + \langle y_e z \mid z \neq y_e, y_{e-2} \rangle.$
Furthermore, $\deg u = 2, \deg y_i = i$.
\todo{Note that here there is a quartic generator of $I$ in degree 12, providing exceptions to minimality by quadrics and an exception to the relation bound when $e = 5$.}
\end{example}
\fi

@@

\begin{thm}
\label{thm:g_1_generators_relations}
Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$,
so that $\sx$ has signature $\sigma = (1; e_1, \ldots, e_r; \delta)$.
If $g = 1$, then the canonical ring
\begin{align*}
	R(\sx, \Delta, \halfcan) = \bigoplus_{d = 0}^\infty H^0(\sx, \sco(L)^{\otimes d})
\end{align*}

\noindent
is generated as a $k$-algebra by elements of degree at most $\max(5, e_1, \ldots, e_r)$ and has minimal relations in degree at most $2e,$ so long as $\sigma$ does not lie in a
finite list of exceptional cases, as listed in Table
~\ref{table:g-1-exceptional}.
\end{thm}

\begin{proof}

\vskip.1in
\noindent
{\sf Case 1: $\Delta > 0$}

If $\Delta > 0$, we must have $\Delta \geq 2$. In this case, let $L_X \in \di X$ be so that $2L_X \sim K_X + \Delta$. We have $\deg L_X \geq 1$, so, by Riemann--Roch, $h^0(\sx,L) \geq 1.$ Therefore, $L$ is linearly equivalent to an effective divisor, so without loss of generality, we may assume $L$ is an effective divisor. We know the theorem holds for $L' = 0$ by Example ~\ref{eg:base-1-0}.
\todo{fix this to accomodate the possibility that $P \in supp(L')$, this has already been done suppose ~\ref{lem:deg1-sat-ind} accommodates it}

We first now show the theorem holds for $L_X$ by induction. Assume it holds for $L' \in \di X$, with $L'$ effective. We will show it holds for $L' + P$. There are two cases, depending on whether $P$ is a basepoint of $L'$.

First, if $P$ is not a basepoint of $L',$ then the hypotheses of Lemma ~\ref{lem:deg1-sat-ind}. In particular, we may take $u \in h^0(\sx,L)$ with $u \neq 0$ and $\ord_P(u) = \lfloor L|_P \rfloor $ with $\ord_P(u) = 0$, as $P$ is not a basepoint of $L'$. Furthermore, Equation ~\ref{eqn:deg1-sat-ind} is satisfied by Riemann Roch, since $\deg L' \geq 1.$ Therefore, by Lemma ~\ref{lem:deg1-sat-ind}, the theorem holds for $L= L'+P$.

Second, if $P$ is a basepoint of $L'$, then the hypotheses of Lemma ~\ref{lem:sat-two-induction-high-genus} are satisfied since $\deg 3(L'+P) \geq 2$ as $\deg L' + P \geq 1$. Therefore, by Lemma ~\ref{lem:sat-two-induction-high-genus}, the theorem holds for $L = L'+P$. This shows the theorem holds for $L_X$.

To complete the case that $\Delta > 0$, we only need show the theorem holds for $L$, assuming it holds for $L_X$. By induction, it suffices to show that if the theorem holds for a divisor $L'$ with $\deg \lfloor L' \rfloor > 0$, then it holds for $L' + \subhalf {e_i}P_i,$ with $e_i$ odd. Similarly to the above, if $P$ is not a basepoint of $L'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by emma ~\ref{lem:deg1-sat-ind}, while if $P$ is a basepoint of $L'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-two-induction-high-genus}.

\vskip.1in
\noindent
{\sf Case 2: $\Delta = 0$}

Since $\Delta = 0$, we may write $L = L_X + \sum_{i=1}^{r}\subhalf{e_i}P_i.$ There are now two further subcases, depending on whether $L_X = 0$ or $L_X = P-Q$ for $P$ and $Q$ two distinct hyperelliptic fixed points.

\vskip.1in
\noindent
{\sf Case 2a: $L_X = P-Q, P \neq Q$}

Note that we are assuming $L$ is not one of the exceptional cases listed in Table ~\ref{table:g-1-exceptional}, so we may either assume $\sx$ has 1 stacky point with $e_1 > 5$ or at least 2 stacky points
